\section{Assignment description}

The assignment is here to show what happens in the real world projects.
It shows and teaches us how to communicate during a project, and how to handle it.

Because of this we as a team need to: communicate, work together, plan and organize.
Besides teamwork, it teaches us new concepts like git and web development.
To pass this course we need to have good collaboration and understand the given rubric, and deliver on those criteria given in said rubric.

To go into more detail, we will make an app that automatically splits the costs of an event among a group.
The parts of the project making this work can be split roughly into three parts:
    - Server side code
    - Client side code
    - Jakarta persistence models

The Server side code is the code that handles all requests from the clients that come from the Client side code.
It handles interactions with the database, and connects clients together in events and remembers which person is which, and much more.

The Client side code sends mostly requests to the server, then the server responds with information that was asked for.
After that the Client side code will show that information in a user-friendly graphical interface, which the client can then interact with.
And of course the client will remember some information, such as recent viewed events.

The Jakarta persistence models are models that correspond with the database schema, such that the server can use these models to interact with the database correctly, thus making sure the database stays intact.
These models also make it easier to send data around, they are somewhat comparable to java object, they even look like it.
By doing this you make the code more readable, and you have a container to put data in and send around in the code.


Then the Teamwork part.
We hold weekly meetings to share information between us, for example telling what went good or what we need to work on.
Also, during these meetings we can make decisions about the project, ensuring we make them together.
To collaborate outside the meetings we use multiple platforms, such as Mattermost and Gitlab.
