\section{Planning}

When it comes to the planning, we first schedule meeting and discuss all points in the project which are required to implement.

The extremely important thing is that everyone have the same and right level of understanding in terms of project structure and project's frameworks.
We always try to ask each other detailed questions to verify that everyone follows the same track.
This is extremely important since the same level of right understanding helps us to make adequate goals and
plan our strategy for the current week which sequentially allows everyone to finish their work on time.

Only after aforementioned stage we begin with actual planning on the meeting.
We first decide how we should distribute the work between people since 6 people working on the same feature is really hard and unnecessary in this project.
However, this does not mean that each person or subgroup only cares about its current work since again staying
on the same track throughout the whole course helps making reasonable decisions in planning.

After distribution we analyze the dependencies between works. Since one subgroup might wait for the completed work of another subgroup,
it is important to understand whether such dependencies might take a place in planning considering world realities and deadlines.
After that we usually draw a schema with all roles' distribution and tasks assigned to each subgroup.
Moreover, we always like to complement our planning with some visualizations.

Then we need to find out whether our planning is flexible.
Something always can go wrong during the work week and we might adjust our planning due to the external circumstances.
if our planning is not flexible enough, then some people might end up not finishing their work which is understandably not desired result.

We decided to keep it flexible when it comes to the final say in the final deliverable and submits. Why not keep it flexible
when we have enough self-organised people in the team.

Also, we should not neglect the power of GitLab when it comes to the planning. Such powerful as issues, milestones and labels
help team track all current problems, workflows and navigate in the whole project.